---
title: "R Notebook"
output: html_notebook
---

My hunch, from the cyanobacteria and SAR11 exemplars is that most/all ostensibly free living bacteria end up on particles in this system. Perhaps because they aggregate with paricles -- that is everything sticks to everything.

How can I test whether this is the case.

Steps:
   *  Identify bacteria that are abundant and free living (eg > 1% in the 0.2 fraction) in each sample
   * Quantify their abundance on the other size fractions; same sample
   * Identify whether each goes to zero on some size fraction.
   * If so, what is the mean abundance threshold where this doesn't happen.
   
```{r}
library(tidyverse)
library(cowplot)
source("InitialProcessing.R")
source("ChesapeakePersonalLibrary.R")
```

```{r}
onePercenters <- nonSpikes %>% 
  select(ID, Station, Size_Class, Depth, ASV, RA) %>%
  filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  filter(Depth == "Surface") %>%
  filter(Size_Class == 0.2, RA > 0.01) %>%
  pull(ASV) %>% unique()
onePercenters
```
There are only ~41 ASV that show up ever with at least 1% relative abundance

```{r}
nonSpikes1pct
```


```{r}
nonSpikes1pct <- nonSpikes %>% filter(ASV %in% onePercenters)
```

```{r}
nonSpikes1pct %>% filter(Depth == "Surface") %>% 
  #filter(ASV == "ASV_2") %>%
  filter(Tag == "Clade_III") %>%
  filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  arrange(Size_Class) %>%
  ggplot(aes(y = copiesPerL/Bin_Size, x = Size_Class, fill = as.factor(Station), shape = as.factor(Station))) +
  scale_y_log10nice(omag = seq(-10, 20, by = 2)) + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_wrap(~ASV) +
  geom_point(size = 3) +
  geom_path(aes(color = as.factor(Station))) +
  scale_shape_manual(values = rep(21:25, 2)) +
  scale_fill_viridis_d(option = "plasma") +
  scale_color_viridis_d(option = "plasma") +
  theme_bw(base_size = 14) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  labs(y = "16s Copies/L/mm", x = expression(paste("Particle Size (", mu, "m)")), fill = "Station", color = "Station", shape = "Station")
```

```{r}
nonSpikes1pct %>% filter(Depth == "Surface") %>% 
  filter(ASV == "ASV_2") %>%
  filter(Tag == "Clade_III") %>%
  filter(Station %in% c(3.1)) %>%
  arrange(Size_Class) 
```

Ok, there are bacteria that are not on *some* size fractions of particles.
What about ones that are on 0.2 but not 1.2?

```{r}
check12 <- nonSpikes %>% 
  select(Station, Size_Class, Depth, ASV, RA) %>%
  filter(Size_Class %in% c(0.2, 1.2)) %>%
  pivot_wider(names_from = Size_Class, values_from = RA) %>%
  filter(!is.na(`0.2`) & !is.na(`1.2`)) %>%
  #filter(`0.2` > .03, `1.2` == 0) # never happens at 3%, happens 4 times at 1%
check12
```

