---
title: "R Notebook"
output: html_notebook
---

Goal here is to get breakaway richness and evenness from all of the samples. 

```{r}
library(breakaway)
library(flextable)
library(ftExtra)
source(here::here("RLibraries", "ChesapeakePersonalLibrary.R"))
#source(here::here("RScripts", "InitialProcessing_3.R"))
#load(here::here("RDataFiles", "InitialProcessing_3.RData"))
#
## Too many random things loaded from the main environent. Speed up may be too much work.
load(here::here("RDataFiles", "InitialProcessing_3_minimal.RData"))
# load(here::here("RDataFiles", "nonSpikes.RData"))
# load(here::here("RDataFiles", "microbialAbundance.RData"))
my_sizes <- sort(unique(microbialAbundance$Size_Class))
```
Breakaway uses frequency tables
```{r}
otuTable <- nonSpikes %>% select(ID, ASV, reads) %>% pivot_wider(names_from = ASV, values_from = reads, id_cols = ID)

otuMatrix <- otuTable %>% column_to_rownames(var = "ID") %>% as.matrix %>% t()

otuPhyseq <- phyloseq::otu_table(otuMatrix, taxa_are_rows = FALSE)

frequencytablelist <- build_frequency_count_tables(otuMatrix)
```

```{r}
plot(breakaway_nof1(frequencytablelist[[1]]))
```
Run the breakaway claculations
```{r}
allBreak <- breakaway(otuPhyseq)

richSummary <- summary(allBreak)

richSummaryExpanded <- richSummary %>% left_join(sampleData, by = c("sample_names" = "ID"))
```

A plot of breakaway richness at each station-depth
```{r fig.height = 8, fig.width = 6}
richSummaryExpanded %>%
  arrange(Size_Class) %>%
  filter(Depth != "Oxy") %>%
  ggplot(
  aes(x = Size_Class, y = estimate,
      fill = as.factor(Station), shape = as.factor(Station))) +
  scale_y_log10nice() + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_grid(Station~Depth) +
  geom_point(aes(size = model)) +
  geom_segment(aes(x = Size_Class, xend = Size_Class, y = lower, yend = upper, color = as.factor(Station))) +
  geom_path(aes(color = as.factor(Station))) +
  scale_shape_manual(values = rep(21:25, 2)) +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```

So no imediatly observavle richness patterns, except maybe that the big particles at the surface of station 3.1 are lower than their friends

As above plot but formatted differently
```{r fig.height = 4, fig.width = 6}
richSummaryExpanded %>%
  arrange(Size_Class) %>%
  filter(Depth != "Oxy") %>%
  ggplot(
  aes(x = Size_Class, y = estimate,
      fill = as.factor(Station), shape = as.factor(Station))) +
  scale_y_log10nice() + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_grid(Depth~.) +
  geom_point(size = 3) +
  geom_segment(aes(x = Size_Class, xend = Size_Class, y = lower, yend = upper, color = as.factor(Station)), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both")) +
  geom_path(aes(color = as.factor(Station))) +
  labs(x = "Size Class (μm)", y = "Richness (Species)") +
  scale_shape_manual(values = rep(21:25, 2)) +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme_bw(base_size = 14) +
  theme(axis.text.x = element_text(angle = 90), legend.position = "none")
```

# Betta
The betta model in breakaway looks for trends in the data

```{r}
myBet <- betta(
  formula = estimate ~ log(Size_Class) + I(log(Size_Class) ^2) + lat +  I(lat^2) + depth,
  ses = error,
  data = richSummaryExpanded %>% filter(depth != "Oxy")
)
```

```{r}
myBet$table
```

Apparenlty, there is a statistical effect for everything except size.

Wait, with the non linear size class, I'm actually significant on everything!
Holy cow.

Apparently my R2 is like 15 percent so no wonder everything looks terrible

# A prettier table of the results
```{r}



myBet$table %>% as.data.frame() %>% rownames_to_column(var = "Parameter") %>%
  mutate(Estimates = format(Estimates, digits = 2, scientific = TRUE) %>%
           reformat_sci()
         ) %>%
  mutate(`Standard Errors` = format(`Standard Errors`, digits = 2, scientific = TRUE) %>%
           reformat_sci()
  ) %>%
  mutate(`p` = if_else(`p-values` < 0.001, "<0.001", paste(" ", as.character(`p-values`)))) %>%
  select(-`p-values`) %>%
  #mutate(Parameter = str_remove_all(Parameter, "I\\(|^\\(|\\)$")) %>% # why won't it remove left facing parentheses
  #mutate(Parameter = str_remove(Parameter, "\\)")) %>%
  mutate(Parameter = str_replace(Parameter, "^I?\\((.*)\\)", "\\1"),
         Parameter = str_replace(Parameter, "\\^2", "\\^2\\^"),
         Parameter = str_replace(Parameter, "depth", "Depth"),
         Parameter = str_replace(Parameter, "lat", "Latitude"),
         Parameter = str_replace(Parameter, "_", " ")# BOOKMARK!!
         ) %>%
  flextable() %>%
  colformat_md() %>%
  identity()
```

## How does the model look if I just linearly regress the estemated beta diversity values?
Instead of using the breakawy function

```{r}
breakLm <- lm(estimate ~ log(Size_Class) + I(log(Size_Class) ^2) + lat +  I(lat^2) + depth, data = richSummaryExpanded)
summary(breakLm)
```
Same overall pattern with less statistical significance

I don't think this workbook returns any figures or tables that are directly used in the manuscript. Look in 
ConventialAlpha.Rmd for those data