---
title: "R Notebook"
output: html_notebook
---

The goal here is to use conventional alpha diversity metrics to see how Chao1 richness, shannon diversity and evenness change across samples and to compare those to the values seen using breakaway in the AlphaDiversity.Rmd file

# Setup
Run AlphaDiversity in scratchnotebooks
That file calculates richness in breakawy which I will combine here
```{r}
#source(here::here("RScripts", "InitialProcessing_3.R"))
source(here::here("RLibraries", "ChesapeakePersonalLibrary.R"))
ksource(here::here("ActiveNotebooks", "BreakawayAlphaDiversity_Env.Rmd"))
```

```{r}
library(vegan)
library(cowplot)
library(flextable)
library(ftExtra)
```



This file is dedicated to conventional, non div-net/breakaway stats, since breakaway seems to choke on this data.

Reshape back into an ASV matrix, but this time correcting for total abundance


```{r}
raDf <- nonSpikes_Remake %>% pivot_wider(id_cols = ID, names_from = ASV, values_from = RA, values_fill = 0)
raMat <- raDf %>% column_to_rownames("ID")
```

```{r}
raMat1 <- raMat %>% as.matrix()
```

```{r}
countMat <-  nonSpikes_Remake %>%
  pivot_wider(id_cols = ID, names_from = ASV, values_from = reads, values_fill = 0) %>%
  column_to_rownames("ID") %>% as.matrix()
```

```{r}
seqDep <- countMat %>% apply(1, sum)
names(seqDep) <- rownames(countMat)
min(seqDep)
```
This value is lower than the lowist chimera checked value because the spikes have been discarded (while chimera checked read depth still has spikes)

```{r}
sampleRichness <- rarefy(countMat, min(seqDep))
```

rarefy everything to the minimum depth (852)
```{r}
countRare <- rrarefy(countMat, min(seqDep))
```

Gamma diversity
```{r}
specpool(countRare)
```

 Doesn't finish

```{r}
#specpool(countMat)
```

# Calculate diversity indeces
All richness estimates
```{r}
richnessRare <- estimateR(countRare)
```

Shannon diversity
```{r}
shan <- diversity(countRare)
shan
```
Evenness
```{r}
pielouJ <- shan/richnessRare["S.chao1",]
pielouJ
```
## Combine diversity data
```{r}
diversityData <- sampleData %>% 
  left_join(richnessRare %>% t() %>% as.data.frame() %>% rownames_to_column("ID"), by = "ID") %>%
  left_join(shan %>% enframe(name = "ID", value = "shannonH"), by = "ID") %>%
  left_join(pielouJ %>% enframe(name = "ID", value = "pielouJ"), by = "ID") %>%
  arrange(Size_Class)
```


# Generate plots of diversity estimates

Parameters for all plots
```{r}
plotSpecs <- list(
  facet_wrap(~Depth, ncol = 1) ,
  theme_bw(base_size = 16) ,
  geom_point(size = 4) ,
  geom_path(aes(color = as.factor(Station))) ,
  scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) ,
  #scale_y_log10nice() ,
  scale_shape_manual(values = rep(21:25, 2)) ,
  scale_fill_viridis_d(option = "plasma") ,
  scale_color_viridis_d(option = "plasma") ,
  labs(x = expression(paste("Particle Size (", mu, "m)"))) ,
  theme(legend.position = "none",
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = .5),
        axis.title.y = element_text(margin = unit(c(3, 3, 3, 3), "mm"), vjust = 0))
)
```

Observed species counts, on rarefied data
```{r}
plotObs <- diversityData %>%
#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = S.obs, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +ylab("Observed ASVs (Rarefied)")#+ scale_y_log10()
plotObs
```
Estemated Chao1 Richness
```{r}
plotChao1 <- diversityData %>%
#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = S.chao1, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +
  geom_errorbar(aes(ymin = S.chao1 -2 * se.chao1, ymax = S.chao1 + 2* se.chao1), width = -.1) + 
  scale_y_log10() +
  ylab("Richness (Chao1)")
plotChao1
```


Shannon diversity
```{r}
plotShan <- diversityData %>%
#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = shannonH, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +
  ylab("Diversity (Shannon H)") +
  lims(y = c(2.5, 6))
plotShan
```

Evenness
```{r}
plotPielou <- diversityData %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pielouJ, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +scale_y_log10() +ylab("Evenness (PielouJ)")
plotPielou
```
All plots together
```{r fig.width = 11, fig.height = 4}
plotAlpha <- plot_grid(plotObs, plotChao1, plotShan, plotPielou, nrow = 1, labels = LETTERS)
plotAlpha
ggsave(here::here("Figures", "ConventionalAlpha.png"), plotAlpha, width = 11, height = 4)
```


## Do we see trends with lat and size?

## Observed Species
Rarefied observed species numbers

```{r}
obsMod <- lm(S.obs ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2)  + Salinity + I(Salinity^2) + Oxygen, data = diversityData %>% mutate(Oxygen = log10(Oxygen + 0.03)))
summary(obsMod)
```

## Richness
Rarified chao1 estimates
```{r}
chao1Mod <- lm(S.chao1 ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2)  + Salinity + I(Salinity^2) + Oxygen, data = diversityData %>% mutate(Oxygen = log10(Oxygen + 0.03)))
summary(chao1Mod)
```
As above but without latitude and depth
```{r}
chao1ModSimple <- lm(S.chao1 ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2), data = diversityData %>% mutate(Oxygen = log10(Oxygen + 0.03)))
summary(chao1ModSimple)
```

## Shannon Diversity

```{r}
shanMod <- lm(shannonH ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2) + Salinity + I(Salinity^2) + Oxygen, data = diversityData %>% mutate(Oxygen = log10(Oxygen + 0.03)))
```


```{r}
summary(shanMod)
```
## Evenness

```{r}
pielouMod <- lm(pielouJ ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2) + Salinity + I(Salinity^2) + Oxygen, data = diversityData %>% mutate(Oxygen = log10(Oxygen + 0.03)))
summary(pielouMod)
```


uomisto H (2010a). “A diversity of beta diver-
sities: straightening up a concept gone awry. 1.
Defining beta diversity as a function of alpha and
gamma diversity.” Ecography, 33, 2–2

# Prediction plots 

## Observed Species

```{r}
predict(obsMod, se.fit = TRUE)
diversityData$pred_obs = predict(obsMod, se.fit = TRUE)$fit
diversityData$se_obs = predict(obsMod, se.fit = TRUE)$se.fit
```

```{r}
plotSpecs2 <- list(
  facet_wrap(~Depth, ncol = 1) ,
  theme_bw(base_size = 16) ,
  #geom_point(size = 4) ,
  geom_path(aes(color = as.factor(Station))) ,
  scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) ,
  #scale_y_log10nice() ,
  scale_shape_manual(values = rep(21:25, 2)) ,
  scale_fill_viridis_d(option = "plasma") ,
  scale_color_viridis_d(option = "plasma") ,
  labs(x = expression(paste("Particle Size (", mu, "m)"))) ,
  theme(legend.position = "none",
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = .5),
        axis.title.y = element_text(margin = unit(c(3, 3, 3, 3), "mm"), vjust = 0))
)
```

```{r}
plotObs_pred <-  diversityData %>%
#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pred_obs, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_obs - 2 * se_obs, yend = pred_obs + 2 * se_obs, xend = Size_Class, color = as.factor(Station)), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"), alpha = 0.5)  +
  plotSpecs2 + ylab("Predicted  ASVs") 
plotObs_pred
```

## Richness

```{r}
predict(chao1Mod, se.fit = TRUE)
diversityData$pred_chao1 = predict(chao1Mod, se.fit = TRUE)$fit
diversityData$se_chao1 = predict(chao1Mod, se.fit = TRUE)$se.fit
```

```{r}
plotChao1_pred <-  diversityData %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pred_chao1, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_chao1 - 2 * se_chao1, yend = pred_chao1 + 2 * se_chao1, xend = Size_Class, color = as.factor(Station)), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"), alpha = 0.5)  +
  plotSpecs2 + ylab("Predictd Richness (Chao1)") + scale_y_log10()
plotChao1_pred
```

## Shannon Diversity
```{r}
predict(shanMod, se.fit = TRUE)
diversityData$pred_shanH = predict(shanMod, se.fit = TRUE)$fit
diversityData$se_shanH = predict(shanMod, se.fit = TRUE)$se.fit
```

```{r}
plotShannonH_pred <- diversityData %>%

 #filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pred_shanH, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_shanH - 2 * se_shanH, yend = pred_shanH + 2 * se_shanH, xend = Size_Class, color = as.factor(Station)), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"),  alpha = 0.5)  +
  plotSpecs2 + ylab("Predicted Diversity (Shannon H)") #+ scale_y_log10()
plotShannonH_pred
```

## Evenness
```{r}
predict(pielouMod, se.fit = TRUE)
diversityData$pred_pielouJ = predict(pielouMod, se.fit = TRUE)$fit
diversityData$se_pielouJ = predict(pielouMod, se.fit = TRUE)$se.fit
```




```{r}
plot_pielouJ_pred <- diversityData %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pred_pielouJ, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_pielouJ - 2 * se_pielouJ, yend = pred_pielouJ + 2 * se_pielouJ, xend = Size_Class, color = as.factor(Station), alpha = 0.5), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"))  +
  plotSpecs2 + ylab("Predicted Evenness (Pielou J)") + scale_y_log10()
plot_pielouJ_pred
```

## Combined prediction plot

```{r fig.width=11, fig.height=4}
plotPredictions <- plot_grid(plotObs_pred, plotChao1_pred, plotShannonH_pred, plot_pielouJ_pred, nrow = 1, labels = LETTERS)
plotPredictions
ggsave(here::here("Figures", "ConventionalAlphaPredictions_Env.png"), plotPredictions, width = 11, height = 4)
```

## Even combindeder

```{r fig.width=11, fig.height = 8}
plot_grid(plotObs, plotChao1, plotShan, plotPielou,
          plotObs_pred, plotChao1_pred, plotShannonH_pred, plot_pielouJ_pred,
          nrow = 2, labels = LETTERS)
```

# Combined summary table

```{r}
alphaSummary <- tibble(
  metric = c("Observed ASVs", "Richness (Chao1)", "Diversity (Shannon H)", "Evenness (Pielou J)"),
  model = list(obsMod, chao1Mod, shanMod, pielouMod)
)

alphaSummary <- alphaSummary %>%
  mutate(df = map(model, ~broom::tidy(summary(.))))

alphaSummary <- alphaSummary %>%
  select(-model) %>%
  unnest(df)

alphaSummary <- alphaSummary %>%
  rename(Metric = metric, Term = term, Estimate = estimate, `Standard Error` = std.error, `T Value` = statistic, p = p.value) %>%
  mutate(Term = str_replace(Term, "^I?\\((.*)\\)", "\\1"),
         Term = str_replace(Term, "\\^2", "\\^2\\^"),
         Term = str_replace(Term, "depth", "Depth"),
         Term = str_replace(Term, "lat", "Latitude"),
         Term = str_replace(Term, "_", " ")# BOOKMARK!!
         ) %>%
  mutate(Estimate = format(Estimate, digits = 2, scientific = TRUE) %>%
           reformat_sci()
         ) %>%
  mutate(`Standard Error` = format(`Standard Error`, digits = 2, scientific = TRUE) %>%
           reformat_sci()
  ) %>%
  mutate(`T Value` = format(`T Value`, digits = 2, scientific = FALSE)) %>%
  mutate(p = if_else(p < 0.001, "< 0.001", format(round(p, digits = 3)))) %>%
  rename(`Standard\nError` = `Standard Error`) %>%
  identity()

alphaSummary %>% flextable() %>% merge_v(j = 1) %>% theme_vanilla() %>%
  bold(i = ~ p< 0.05, j = "p") %>%
  colformat_md() %>%
  set_table_properties(layout = "autofit") %>%
  align(j = -c(1:2), align = "right")
```

# Now considering breakaway values

```{r}
richSummary %>% rename_(.dots = setNames(names(.), paste0('break_', names(.))))
```


```{r}
diversityDataWB <- full_join(diversityData,
                             richSummary %>% rename_(.dots = setNames(names(.), paste0('break_', names(.)))),
                             by = c("ID" = "break_sample_names"), suffix = c("", "_break")) %>%
  mutate(pielouJ2 = shannonH/break_estimate) %>%
  identity()
```


```{r}
diversityDataWB
```
```{r}
pielouMod2 <- lm(pielouJ2 ~ sqrt(Size_Class) + I(sqrt(Size_Class)^2) + Salinity + I(Salinity^2) + Oxygen, data = diversityDataWB %>% mutate(Oxygen = log(Oxygen + 0.03)))
summary(pielouMod2)
```
Ok. So the narrative makes sense. Alpha diveristy is driven by variability in richness rather than evenness.
Why would we see an effect in chao1 but not breakaway? Because chao1 is more driven by abundant stuff that makes the rarification threshold. 
My first hunch is that chao1 responds to evenness, but actually that shouldn't have any effect since there is no evenness variability? Or maybe just that breakaway is more variable (because it detects fine level differences in rare species) and that doesn't map as nicely with overall patterns.

```{r}
plotBreak <- diversityDataWB %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = break_estimate, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +
  #scale_y_log10()+
  ylab("Richness (Breakaway)")
plotBreak
```


```{r}
plotPielou2 <- diversityDataWB %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pielouJ2, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +
  #scale_y_log10()+
  ylab("Evenness (PielouJ)")
plotPielou2
```

## Redo predictions for good measure

```{r}
predict(pielouMod2, se.fit = TRUE)
diversityDataWB$pred_pielouJ2 = predict(pielouMod2, se.fit = TRUE)$fit
diversityDataWB$se_pielouJ2 = predict(pielouMod2, se.fit = TRUE)$se.fit
```


```{r}
plot_pielouJ2_pred <- diversityDataWB %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = pred_pielouJ2, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_pielouJ2 - 2 * se_pielouJ2, yend = pred_pielouJ2 + 2 * se_pielouJ2, xend = Size_Class, color = as.factor(Station), alpha = 0.5), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"))  +
  plotSpecs2 + ylab("Predicted Evenness (Pielou J2)") #+ scale_y_log10()
plot_pielouJ2_pred
```

## Breakaway richness subplots

```{r}
plotBreakaway <- diversityDataWB %>%
#filter(Depth %in% c("Surface", "Bottom")) %>%
  ggplot(aes(x = Size_Class, y = break_estimate, shape = as.factor(Station), fill = as.factor(Station))) +
  plotSpecs +
  geom_errorbar(aes(ymin = break_lower, ymax = break_upper), width = -.1) + 
  scale_y_log10() +
  ylab("Richness (Breakaway)")
plotBreakaway
```
```{r}
#predict(breakLm, se.fit = TRUE)
# doesn't work because built with a different data frame
```

Why are these not smooth curves?!! 
What if I redo the model, this time with the same data frame

```{r}
breakLm2 <- lm(break_estimate ~ sqrt(Size_Class) + I(sqrt(Size_Class) ^2) + Salinity +  I(Salinity^2) + Oxygen ,data = diversityDataWB %>% mutate(Oxygen = log10(Oxygen + 0.03)))
breakLm2 %>% summary()
```
Note the non statistical significance overall

```{r}
#predict(breakLm2, se.fit = TRUE)
diversityDataWB$pred_break = predict(breakLm2, se.fit = TRUE)$fit
diversityDataWB$se_break = predict(breakLm2, se.fit = TRUE)$se.fit
```

```{r}
plot_break_pred <- diversityDataWB %>%

#filter(Depth %in% c("Surface", "Bottom")) %>%
#  filter(Station == 4.3) %>%
  ggplot(aes(x = Size_Class, y = pred_break, shape = as.factor(Station), fill = as.factor(Station))) +
  geom_segment(aes(y = pred_break - 2 * se_break, yend = pred_break + 2 * se_break, xend = Size_Class, color = as.factor(Station), alpha = 0.5), arrow = arrow(angle = 70, length = unit(0.05, "in"), ends = "both"))  +
  plotSpecs2 + ylab("Predicted Richness (Breakaway -- LM)") #+ scale_y_log10()
plot_break_pred

```




## Rebuilding combined products



```{r fig.width = 11, fig.height = 4}
plotAlphaWB <- plot_grid(plotBreakaway, plotShan, plotPielou2, nrow = 1, labels = LETTERS)
plotAlphaWB
ggsave(here::here("Figures", "BreakawayAlpha.png"), plotAlphaWB, width = 8, height = 4)
```

Summary table
I want both breakaway metrics here

```{r}
bettaTable <- myBet_Env$table %>% 
  as.data.frame() %>%
  rename(estimate = Estimates,
         `std.error` = `Standard Errors`,
         `p.value`=`p-values`
         ) %>%
  mutate(`statistic` = NA) %>%
  rownames_to_column(var = "term") %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  as_tibble()
bettaTable
```


```{r}
alphaSummary2 <- tibble(
  metric = c("Richness (Breakaway -- LM)", "Diversity (Shannon H)", "Evenness (Pielou J)"),
  model = list(breakLm_Env, shanMod, pielouMod2)
)
  
alphaSummary2 <- alphaSummary2 %>%
  mutate(df = map(model, ~broom::tidy(summary(.))))

## Add in willis variables

breakawaySummary <- tibble(
  metric = "Richness (Breakaway -- Betta)",
  model = NULL,
  df = list(bettaTable)
)

alphaSummary2 = bind_rows(breakawaySummary, alphaSummary2)

alphaSummary2 <- alphaSummary2 %>%
  select(-model) %>%
  unnest(df)

alphaSummary2 <- alphaSummary2 %>%
  rename(Metric = metric, Term = term, Estimate = estimate, `Standard Error` = std.error, `T Value` = statistic, p = p.value) %>%
  mutate(Term = str_replace(Term, "^I?\\((.*)\\)", "\\1"),
         Term = str_replace(Term, "\\^2", "\\^2\\^"),
         Term = str_replace(Term, "depth", "Depth"),
         Term = str_replace(Term, "lat", "Latitude"),
         Term = str_replace(Term, "sqrt\\(Size_Class\\)", "√Size Class"),
         Term = str_replace(Term, "_", " ")# BOOKMARK!!
         ) %>%
  mutate(Estimate = format(Estimate, digits = 2, scientific = TRUE) %>%
           reformat_sci()
         ) %>%
  mutate(`Standard Error` = format(`Standard Error`, digits = 2, scientific = TRUE) %>%
           reformat_sci()
  ) %>%
  mutate(`T Value` = format(`T Value`, digits = 2, scientific = FALSE)) %>%
  mutate(p = if_else(p < 0.001, "< 0.001", format(round(p, digits = 3)))) %>%
  rename(`Standard\nError` = `Standard Error`) %>%
  identity()



alphaSummary2

alphaTable2 <- alphaSummary2 %>% flextable() %>% merge_v(j = 1) %>% theme_vanilla() %>% bold(i = ~ p< 0.05, j = "p") %>% colformat_md() %>% set_table_properties(layout = "autofit") %>%
  align(j = -c(1:2), align = "right")
alphaTable2

alphaTable2 %>% save_as_docx(path = here::here("Tables", "alphaTable2_Env.docx"))
```

myBet$table

## And finally predictions from richness, diversity evenness again.


```{r fig.width = 11, fig.height = 4}
plotAlphaWB_pred <- plot_grid(plot_break_pred,plotShannonH_pred,plot_pielouJ2_pred, nrow = 1, labels = LETTERS)
plotAlphaWB_pred
```

```{r}
ggsave(here::here("Figures", "BreakawayAlphaPredictions_Env.png"), plot = plotAlphaWB_pred, width = 8, height = 4)
```

