---
title: "R Notebook"
output: html_notebook
---

The goal of this notebook is to generate some example plots of how relative abundance
is related to (less useful than) concentration and density.

I think a good ASV is Pirellulaceae;14 -- aka ASV_14 a Planktomycetes. 
It follows the standard particle attached paradoxical distribution (dense on big particles, mostly on small particles)

```{r}
library(here)
library(tidyverse)
source(here("RLibraries", "ChesapeakePersonalLibrary.R"))
#load(here("RDataFiles", "InitialProcessing_3.RData"))
load(here("RDataFiles", "InitialProcessing_3_minimal.RData"))

```

Our target bacteria
{No longer works because the asvs got renmbered when I added the last batch of samples}
I want a paracoccus ASV that has a regualr abundance pattern
To do *after* the brigandine plots.

I want one of the planktos
```{r}
nonSpikes20 %>%
  filter(Family == "Pirellulaceae", Station == 3.3, Depth == "Bottom", Size_Class == 5) %>%
  arrange(-copiesPerL)
```


```{r}
```


```{r}
target <- nonSpikes20 %>%
  #filter(ASV == "ASV_14")
  #filter(nASV %in% c(14, 17, 47, 48))
  filter(nASV == 13)
  #filter(nASV %in% c(459))
target %>% head
```

```{r}
target %>%
  #filter(Depth != "Oxy") %>%
  arrange(Size_Class) %>%
  ggplot(aes(x = Size_Class, y = RA, fill = as.factor(Station), shape = as.factor(Station))) + facet_wrap(~Depth, nrow = 2) +
  geom_point() +
  ches_plot_options
```
```{r fig.height=4, fig.width = 2.5}
target %>%
  filter(Depth == "Bottom") %>%
  mutate(copiesPerMg = copiesPerL/MassperLiter) %>%
  pivot_longer(cols = c("RA", "copiesPerL", "copiesPerMg"), names_to = "metric", values_to = "abund") %>%
  arrange(Size_Class) %>%
  ggplot(aes(x = Size_Class, y = abund, shape = as.factor(Station), fill = as.factor(Station))) + 
  facet_grid(metric~ Tag_ASV, scales = "free_y") +
  ches_plot_options
```

```{r}


log_breaks_fn <- function(bob){
  minBob <- min(bob)
  maxBob <- max(bob)
  prang = 10^floor(log10(minBob))
  bls <- NULL
  while(prang < maxBob){
    lorder <- floor(log10(prang))
    loc_seq <- seq(from = 10^lorder, to = 10^(lorder + 1), by = 10^lorder)
    bls <- c(bls, loc_seq)
    prang <- 10^(lorder + 1)
  }
  bls
}
```


```{r}
library(ecoflux)
```

```{r}
scientific_10 <- function(x) {
    xout <- gsub("1e", "10^{", format(x),fixed=TRUE)
    xout <- gsub("{-0", "{-", xout,fixed=TRUE)
    xout <- gsub("{+", "{", xout,fixed=TRUE)
    xout <- gsub("{0", "{", xout,fixed=TRUE)
    xout <- paste(xout,"}",sep="")
    return(parse(text=xout))
}
```

```{r fig.height=2, fig.width = 3.5}
plt1 <- target %>%
  filter(Depth == "Oxycline", Station == 3.3) %>%
  #filter(Depth == "Bottom", Station == 3.3) %>%
  mutate(RA = RA * 100) %>%
  mutate(copiesPerMg = copiesPerL/MassperLiter) %>%
  mutate(copiesPerParticle = copiesPerL/ParticlesPerLiter) %>%
  pivot_longer(cols = c("RA", "copiesPerL", "copiesPerMg", "copiesPerParticle"), names_to = "metric", values_to = "abund") %>%
  arrange(Size_Class) %>%
  mutate(metric = factor(metric, levels = c("RA", "copiesPerMg", "copiesPerL", "copiesPerParticle"))) %>%
  mutate(metric = fct_recode(metric, "Rel. Abun. (%)" = "RA", "Copies/mg" = "copiesPerMg", "Copies/L" = "copiesPerL", "Copies/Particle"= "copiesPerParticle")) %>%
  ggplot(aes(x = Size_Class, y = abund)) + 
  facet_wrap(~metric, scales = "free_y", strip.position = "right") +
  geom_point(color = "Black") + geom_path() +
  #scale_y_log10nice() +
  scale_y_log10(minor_breaks = log_breaks_fn) +
  scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  theme_bw(base_size = 14) +
  ylab(NULL)+ xlab("Size Class") + 
  theme(strip.background = element_blank(),
           strip.placement = "outside",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
plt1
```
```{r}
ggsave(here::here("Figures", "Exemplar_ASV13_CB3.3_Bottom.png"), plot = plt1, height = 3, width = 5)
```




