---
title: "R Notebook"
output: html_notebook
---

My hunch, from the cyanobacteria and SAR11 exemplars is that most/all ostensibly free living bacteria end up on particles in this system. Perhaps because they aggregate with paricles -- that is everything sticks to everything.

How can I test whether this is the case.

Steps:
   *  Identify bacteria that are abundant and free living (eg > 1% in the 0.2 fraction) in each sample
   * Quantify their abundance on the other size fractions; same sample
   * Identify whether each goes to zero on some size fraction.
   * If so, what is the mean abundance threshold where this doesn't happen.
   
To do: Fix the legends so they have the same breaks and labels as everything else.
   
```{r}
library(tidyverse)
library(cowplot)
library(here)
source(here("RLibraries", "ChesapeakePersonalLibrary.R"))
# I had been bringing in all the data and just using one variable, but then I didn't.
env1 <- attach(here("RDataFiles", "InitialProcessing_3.RData"))
#load(here("RDataFiles", "nonSpikes.RData"))
set.seed(10033)
nonSpikes <- env1$nonSpikes
nonSpikes <- nonSpikes %>% mutate(fStation = factor(Station, levels = as.character(c(3.1, 3.2, 3.3, 5.1, 4.3, 5.5))))
my_stations <- nonSpikes$Station %>% unique()
## somewhat to my suprise, variables such as taxa01 appear to be globally available even though they should be only in env1
# I'm going to leave things like this since code runs and I'm running out of steam on this code wrangling
```

```{r}
onePercenters <- nonSpikes %>% 
  select(ID, Station, Size_Class, Depth, ASV, RA) %>%
  # filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  # filter(Depth == "Surface") %>%
  filter(Size_Class == 0.2, RA > 0.01) %>%
  pull(ASV) %>% unique()

onePercenters_Surface <- nonSpikes %>% 
  select(ID, Station, Size_Class, Depth, ASV, RA) %>%
  filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  filter(Depth == "Surface") %>%
  filter(Size_Class == 0.2, RA > 0.01) %>%
  pull(ASV) %>% unique()

onePercenters_Oxycline <- nonSpikes %>% 
  select(ID, Station, Size_Class, Depth, ASV, RA) %>%
  #filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  filter(Depth == "Oxycline") %>%
  filter(Size_Class == 0.2, RA > 0.01) %>%
  pull(ASV) %>% unique()

onePercenters_Bottom <- nonSpikes %>% 
  select(ID, Station, Size_Class, Depth, ASV, RA) %>%
  #filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  filter(Depth == "Bottom") %>%
  filter(Size_Class == 0.2, RA > 0.01) %>%
  pull(ASV) %>% unique()

onePercenters
onePercenters_Surface
onePercenters_Bottom
```



There are only ~41 ASV that show up ever with at least 1% relative abundance

Lets look at their taxonomy
```{r}
onePercentFreeTaxa <- taxa01 %>% filter(ASV %in% onePercenters)
```


```{r}
nonSpikes1pct <- nonSpikes %>% filter(ASV %in% onePercenters)
nonSpikes1pct_Surface <- nonSpikes %>% filter(ASV %in% onePercenters_Surface) # Includes all depths
nonSpikes1pct_Oxycline <- nonSpikes %>% filter(ASV %in% onePercenters_Oxycline)
nonSpikes1pct_Bottom <- nonSpikes %>% filter(ASV %in% onePercenters_Bottom)

```

scale_shape_manual(values = rep(21:25, 2)[3:10]) +
  scale_fill_manual(values = viridis::plasma(n = 6)[3:6]) +
```{r}
surfaceNSPlot <- nonSpikes1pct_Surface %>%

  filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  filter(Depth == "Surface") %>%
  arrange(Size_Class) %>%
  ggplot(aes(y = copiesPerL/Bin_Size, x = Size_Class, fill = fStation, shape = fStation)) +
  scale_y_log10nice(omag = seq(-10, 20, by = 2)) + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_wrap(~Tag_ASV, ncol = 4) +
  geom_point(size = 3) +
  geom_path(aes(color = as.factor(fStation))) +

  ## Manually specify the shapes and colors to match the other plot
  scale_shape_manual(values = rep(21:25, 2)[c(1,2,4)]) +
  scale_fill_manual(values = viridis::plasma(n = 6)[c(1,2,4)]) +
  scale_color_manual(values = viridis::plasma(n = 6)[c(1,2,4)]) +
  theme_bw(base_size = 14) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  labs(y = "16s Copies/L/mm", x = expression(paste("Particle Size (", mu, "m)")), fill = "Station", color = "Station", shape = "Station")  +
  theme(axis.text.x = element_text(angle = 90), strip.text = element_text(size = 8))
surfaceNSPlot
ggsave(here("Figures", "surfaceNS.png"), plot = surfaceNSPlot, height = 8, width = 8.5, limitsize = FALSE)
```

```{r}
oxyclineNSPlot <- nonSpikes1pct_Oxycline %>%

  filter(Station %in% c(3.3, 4.3)) %>%
  filter(Depth == "Oxycline") %>%
  arrange(Size_Class) %>%
  ggplot(aes(y = copiesPerL/Bin_Size, x = Size_Class, fill = fStation, shape = fStation)) +
  scale_y_log10nice(omag = seq(-10, 20, by = 2)) + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_wrap(~Tag_ASV, ncol = 4) +
  geom_point(size = 3) +
  geom_path(aes(color = as.factor(fStation))) +

  ## Manually specify the shapes and colors to match the other plot
  scale_shape_manual(values = rep(21:25, 2)[c(3,4)]) +
  scale_fill_manual(values = viridis::plasma(n = 6)[c(3,4)]) +
  scale_color_manual(values = viridis::plasma(n = 6)[c(3,4)]) +
  theme_bw(base_size = 14) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  labs(y = "16s Copies/L/mm", x = expression(paste("Particle Size (", mu, "m)")), fill = "Station", color = "Station", shape = "Station")  +
  theme(axis.text.x = element_text(angle = 90), strip.text = element_text(size = 8))
oxyclineNSPlot
ggsave(here("Figures", "oxyclineNS.png"), plot = oxyclineNSPlot, height = 8, width = 8.5, limitsize = FALSE)
```

```{r fig.height = 5, fig.width = 5}
bottomNSPlot <- nonSpikes1pct_Bottom %>% filter(Depth == "Bottom") %>% 
  arrange(Size_Class) %>%
  ggplot(aes(y = copiesPerL/Bin_Size, x = Size_Class, fill = as.factor(Station), shape = as.factor(Station))) +
  scale_y_log10nice(omag = seq(-10, 20, by = 2)) + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_wrap(~Tag_ASV, ncol = 4) +
  geom_point(size = 3) +
  geom_path(aes(color = as.factor(Station))) +
 ## Manually specify the shapes and colors to match the other plot
  scale_shape_manual(values = rep(21:25, 2)[-3]) +
  scale_fill_manual(values = viridis::plasma(n = 6)[-3]) +
  scale_color_manual(values = viridis::plasma(n = 6)[-3]) +
  theme_bw(base_size = 12) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  labs(y = "16s Copies/L/mm", x = expression(paste("Particle Size (", mu, "m)")), fill = "Station", color = "Station", shape = "Station") +
  theme(axis.text.x = element_text(angle = 90), strip.text = element_text(size = 8))
bottomNSPlot
ggsave(here("Figures", "bottomNS.png"), plot = bottomNSPlot, height = 11, width = 8.5, limitsize = FALSE)
```


SAR11 surface III clade
```{r}
nonSpikes1pct %>% filter(Depth == "Surface") %>% 
  #filter(ASV == "ASV_2") %>%
  filter(Tag == "Clade_III") %>%
  filter(Station %in% c(3.1, 3.2, 4.3)) %>%
  arrange(Size_Class) %>%
  ggplot(aes(y = copiesPerL/Bin_Size, x = Size_Class, fill = as.factor(Station), shape = as.factor(Station))) +
  scale_y_log10nice(omag = seq(-10, 20, by = 2)) + scale_x_log10(breaks = my_sizes, labels = as.character(my_sizes)) +
  facet_wrap(~ASV) +
  geom_point(size = 3) +
  geom_path(aes(color = as.factor(Station))) +
  scale_shape_manual(values = rep(21:25, 2)) +
  scale_fill_viridis_d(option = "plasma") +
  scale_color_viridis_d(option = "plasma") +
  theme_bw(base_size = 14) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "none") +
  labs(y = "16s Copies/L/mm", x = expression(paste("Particle Size (", mu, "m)")), fill = "Station", color = "Station", shape = "Station")
```

```{r}
nonSpikes1pct %>% filter(Depth == "Surface") %>% 
  filter(ASV == "ASV_3") %>%
  filter(Tag == "Clade_III") %>%
  filter(Station %in% c(3.1)) %>%
  arrange(Size_Class) 
```

Ok, there are bacteria that are not on *some* size fractions of particles.
What about ones that are on 0.2 but not 1.2?

```{r}
check12 <- nonSpikes %>% 
  select(Station, Size_Class, Depth, ASV, RA) %>%
  filter(Size_Class %in% c(0.2, 1.2)) %>%
  pivot_wider(names_from = Size_Class, values_from = RA) %>%
  filter(!is.na(`0.2`) & !is.na(`1.2`)) %>%
  #filter(`0.2` > .03, `1.2` == 0) # never happens at 3%, happens 4 times at 1%
  identity()
check12
```

