---
title: "R Notebook"
output: html_notebook
---

Goal here is to show CTD profiles
Pulled from Emily Dougherty's analysis.
```{r}
library(tidyverse)
library(here)
library(readxl)
library(cowplot)
```
# Loading in Data

```{r}
source(here("RScripts", "CBMap_Transect.R"))
source(here("RLibraries", "ChesapeakePersonalLibrary.R"))
```

Pull in Station Coordinates
```{r}
# stations <- read_csv(here("InputData", "stations.csv"))
# stations01 <- stations %>% mutate(Station = str_sub(Station, start = 3)) %>%
#   mutate(isWest = str_detect(Station, "W")) %>% filter(!isWest) %>% mutate(Station = str_remove(Station, "C")) %>% select(-isWest)
```

CTD Data processed by Sairah Malkin
```{r}
SairahCTD <- read_excel(here("InputData", "Summary CTD 2019-07 cruise CB_Malkin.xlsx"))
```

#Processing the data

```{r}
ParseCTD <- SairahCTD %>%
  mutate(FullStation = Station,
         Station = parse_number(FullStation),
         LastChar = str_sub(FullStation, start = -1, end = -1),
         EWLoc = if_else(LastChar %in% c("E", "W"), LastChar, "C")
         ) %>%
  select(-LastChar)
```

New names
```{r}
CTDNameTibble <- tribble(
  ~ShortName, ~FullName, ~BetterName,
  "Depth", "Depth (m)", "Depth (m)",
  "Temperature", "Temperature (degC)", "Temperature~(degree*C)",
  "Salinity", "Salinity (PSU)", "Salinity~(PSU)",
  "Oxygen", "Oxygen (mg L-1)", "Oxygen~(mg/L)",
  "Fluorescence", "Fluorescence (mg m-3)", "Fluorescence~(mg/m^3)",
  "PAR", "PAR (umol m-2 s-1)", "PAR~(mu*mol/m^2/s)",
  "pH", "pH", "pH"
)
```

Clean up the CTD data
```{r}
UseCTD <- ParseCTD %>%
  filter(EWLoc == "C", is.finite(Station)) %>%
  select(Station,
         Depth = `Depth (m)`,
         Oxygen = `Oxygen (mg L-1)`,
         Temperature = `Temperature (degC)`,
         Salinity = `Salinity (PSU)`,
         Fluorescence = `Fluorescence (mg m-3)`,
         PAR = `PAR (umol m-2 s-1)`,
         pH) %>%
  pivot_longer(cols = -c(Depth, Station)) %>%
  left_join(CTDNameTibble, by = c("name" = "ShortName")) %>%
  mutate(name = ordered(name, levels = CTDNameTibble$ShortName),
         BetterName = ordered(BetterName, levels = CTDNameTibble$BetterName)) 
```



Assign "zones" to depths. Are things from the shallow or the deep region

The following essentially is a table that tells which CTD samples correspond to which depth zones

```{r}
SampleDepths00 <- read_csv(here("InputData", "SampleDepths.csv"))
SampleDepths01 <- SampleDepths00 %>%
  pivot_longer(cols = -Station, names_to = "DepthZone", values_to = "Depth") %>%
  filter(is.finite(Depth)) %>%
  mutate(Depth = -Depth)

SampleWidth = 2 # Precision of CTD in M
SampleDepths02 <- SampleDepths01 %>%
  mutate(Lower = Depth - SampleWidth/2,
         Upper = Depth + SampleWidth/2)
SampleDepths02
```

The zoneify function tels whether a sample is in a particular depth zone
```{r}
zoneify <- function(StationIn, DepthIn, ZoneTable){
  Thing <- ZoneTable %>%
    filter(Station == StationIn) %>%
    mutate(isIn = (DepthIn > Lower & DepthIn < Upper)) %>%
    filter(isIn) %>%
    pull(DepthZone)
  
  if(length(Thing) == 1){
    Thing
  }else{
    NA # This returns NA if multiple or no depths hit
  }
}

zoneify(3.1, 7.11, SampleDepths02) # Corresponding to a bottom sample
zoneify(3.1, 700, SampleDepths02) # Not corresponding to any of our depths
```

Determine which ctd samples correspond to which depth zones
Apparently the following is inefficient and slow (takes about one minute)
```{r}
pt0 <- proc.time() # start time of the slow process
UseCTD01 <- UseCTD %>%
  mutate(Zone = map2_chr(Station, Depth, zoneify, SampleDepths02))
pt1 <- proc.time() # end time of the slow process
opTime <- pt1-pt0 # how long does the process take?
opTime
```

Create what is effectively "bottle" data. CTD averages around where we took our samples.
```{r}
UseCTD02 <- UseCTD01 %>%
  filter(!is.na(Zone)) %>%
  group_by(Station, name, BetterName, Zone) %>%
  summarize(value = mean(value)) %>%
  ungroup() %>%
  left_join(SampleDepths01, by = c("Station", "Zone" = "DepthZone"))
```

```{r}
write_csv(UseCTD02, file = here::here("IntermediateData", "BottleCTD.csv"))
```


### CTD Plots

Most CTD Variables

```{r fig.height = 3, fig.width = 2}
MostPlot <- ggplot(UseCTD %>% filter((name %in% c("Temperature", "Salinity"))), aes(y = Depth, x = value, group = as.factor(Station))) +
  scale_color_viridis_d(option = "plasma") + scale_fill_viridis_d(option = "plasma") +
  scale_shape_manual(values = c(21:25, 21)) +
  geom_path(size = 2, aes(color = as.factor(Station))) +
  geom_path() + 
  facet_wrap(~BetterName, scales = "free_x", strip.position = "bottom", labeller = "label_parsed", nrow = 2) +
  scale_y_reverse(limits = c(33, 0)) +
  theme_cowplot() +
  geom_point(data = UseCTD02 %>% filter((name %in% c("Temperature", "Salinity"))), aes(shape = as.factor(Station), fill = as.factor(Station)), color = "black", size = 3)+
  labs(y = "Depth (m)") +
  theme(strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_text(size = 11),
        axis.title.x = element_blank(),
        legend.position = "none")

MostPlotWLab <- ggdraw(MostPlot) + draw_plot_label(c("B", "C"), x = c(0.3, 0.3), y = c(1, .4), size = 18)

MostPlotWLab
```


```{r fig.height = 5, fig.width = 2}
UseCtdForOx <- UseCTD %>% filter((name %in% c("Oxygen"))) %>%
  mutate(Station = factor(Station, levels = rev(unique(Station))))
StationsLs <- as.character(unique(UseCTD$Station))

OxyPlot <- UseCtdForOx %>%
  ggplot(aes(y = Depth, x = value, group = as.factor(Station))) +
  scale_color_manual(breaks = StationsLs, values = viridis::plasma(n = 6)[1:6]) +
  scale_fill_manual(breaks = StationsLs, values = viridis::plasma(n = 6)[1:6]) +
  scale_shape_manual(breaks = StationsLs, values = c(21:25, 21)[1:6]) +
  geom_path(size = 2, aes(color = as.factor(Station))) +
  geom_path() + 
  facet_wrap(~BetterName, scales = "free_x", strip.position = "bottom", labeller = "label_parsed", nrow = 2) +
  scale_y_reverse(limits = c(33, 0)) +
  theme_cowplot() +
  geom_point(data = UseCTD02 %>% filter((name %in% c("Oxygen"))), aes(shape = as.factor(Station), fill = as.factor(Station)), color = "black", size = 3)+
  #labs(y = "") +
  #lims(y = c(15, 0)) +
  geom_hline(yintercept = 16) + # Add sulfitocline
  annotate("label", x = 6, y = 16, label = "                 ", fill = "white") +
  annotate("text", x = 5.5, y = 16, label = bquote(H[2]*S), fill = "white") +
  annotate("point", x = 6.65,  y = 16, shape = 23, color = "black", fill = viridis::plasma(6)[3], size = 3)+
  annotate("point", x = 7.4,  y = 16, shape = 24, color = "black", fill = viridis::plasma(6)[4], size = 3)+
  theme(strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_text(size = 11),
        axis.title.x = element_blank(),
                axis.title.y = element_blank(),
        legend.position = "none")
OxyPlotWLab <- ggdraw(OxyPlot) + draw_plot_label("D", 0.18, 1, size = 18)
OxyPlotWLab
```

Add Map

```{r}
cbMapWLab <- ggdraw(cbMap) + draw_plot_label("A", 0, 1, size = 18)
```


```{r}
ProfilesWMap <- plot_grid(cbMapWLab, MostPlotWLab, OxyPlotWLab, rel_widths = c(1,1,1), nrow = 1)
ProfilesWMap
```
```{r}
ggsave(here("Figures", "PofilesWithMap.png"), width = 6, height = 4)
```

# Now with sulfide

```{r}
ksource(here::here("ActiveNotebooks", "Sulfide.Rmd"))
```

```{r fig.height = 3, fig.width = 2}
SalinityPlot <- ggplot(UseCTD %>% filter((name %in% c("Salinity"))), aes(y = Depth, x = value, group = as.factor(Station))) +
  scale_color_viridis_d(option = "plasma") + scale_fill_viridis_d(breaks = StationsLs, option = "plasma") +
  scale_shape_manual(values = c(21:25, 21)) +
  geom_path(size = 2, aes(color = as.factor(Station))) +
  geom_path() + 
  facet_wrap(~BetterName, scales = "free_x", strip.position = "bottom", labeller = "label_parsed", nrow = 2) +
  scale_y_reverse(limits = c(33, 0)) +
  theme_cowplot() +
  geom_point(data = UseCTD02 %>% filter((name %in% c("Salinity"))), aes(shape = as.factor(Station), fill = as.factor(Station)), color = "black", size = 3)+
  labs(y = "Depth (m)") +
  theme(strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_text(size = 11),
        axis.title.x = element_blank(),
        legend.position = "none")

SalinityPlotWLab <- ggdraw(SalinityPlot) + draw_plot_label(c("B"), x = c(0.3, 0.3), y = c(1, .4), size = 18)
SalinityPlot
```


#sulfidePlot + lims(y = c(33, 0)) +
```{r}
ProfilesWMapSulfide <- plot_grid(cbMap,
                                 SalinityPlot + lims(y = c(33, 0)),
                                 OxyPlot + lims(y = c(33, 0)),
                                 #theme(plot.margin = margin(t = 6, l = 9, r = 5, b = 17, unit = "pt")),
                                 rel_widths = c(1,1,1), nrow = 1,
                                 labels = LETTERS)
ProfilesWMapSulfide
```

```{r}
ggsave(here("Figures", "PofilesWithMapAndSulfide.png"), width = 8, height = 4)
```


