---
title: "R Notebook"
output: html_notebook
---


#### Old stuff #####

# Constrained ordination with respect to size (all sizes included), conditioned on lat and depth

```{r}
ccaConditionedAllSizes <- cca(wideASVs_log ~ Condition(Depth2 + lat) + sqrt(Size_Class), data = sampleData01)
```

```{r}
CCA_Eigen_Plot(ccaConditionedAllSizes)
```

```{r}
paste("Variance Explained", round(ccaConditionedAllSizes$CCA$eig[1]/ccaConditionedAllSizes$tot.chi, 3) * 100, "%")
anova(ccaConditionedAllSizes, permutations = how(nperm = 10^3 - 1))
```

```{r}

My_Constrained_CCA_Plot <- function(ConditionedCCA){

Fort <- fortify(ConditionedCCA) %>% filter(Score %in% c("sites", "biplot")) %>% # not sure what constraints are
 left_join(microbialAbundance, by = c("Label" = "ID"))

ccaPlot <- Fort %>%
  filter(Score == "sites") %>%
  mutate(Depth = recode(Depth, `Oxy` = "Oxycline")) %>%
  select(Station, Depth, Size_Class, everything()) %>%
  ggplot(aes(x = CCA1, y = CA1,
             fill = as.factor(Station),
             shape = as.factor(Station),
             size = sqrt(Size_Class),
             color = as.factor(Depth)
             )) + 
 geom_point() +
 coord_fixed(sqrt(ConditionedCCA$CA$eig[1]/ConditionedCCA$CCA$eig[1])) +
 geom_text(aes(label = Label, x = CCA1 * 3.5, y = CA1 * 3.5), color = "black",
           data = Fort %>%
             filter(Score == "biplot") %>%
             mutate(Label = recode(Label,
                                   `sqrt(Size_Class)` = "Size"
                                  
                                   ))
             ) +
  geom_segment(aes(x = 0, y = 0, xend  = CCA1 * 3, yend = CA1 * 3), data = Fort %>% filter(Score == "biplot"), inherit.aes = FALSE, size = 1, alpha = 0.5, arrow = arrow(length = unit(0.1, "in"))) +
  #geom_point(aes(x  = CCA1, y = CCA2), data = ccaConstrainedFort %>% filter(Score == "biplot"), inherit.aes = FALSE) +
  labs(x = paste0("CCA1 (", round(ConditionedCCA$CCA$eig[1]/ConditionedCCA$tot.chi, 3) * 100, "%)"),
       y = paste0("CA1 (", round(ConditionedCCA$CA$eig[1]/ConditionedCCA$tot.chi, 3) * 100, "%)"),
       col = "Depth (Outline Color)",
       fill = "Station",
       shape = "Station",
       size = "Size Class") +
  myPlotDetails
ccaPlot
}

AllSizePlot <- My_Constrained_CCA_Plot(ccaConditionedAllSizes)
AllSizePlot
```

# fortification functions for partial

```{r}
# my_fortify_function <- function(ccaConstrained){
#   fortify(ccaConstrained) %>% filter(Score %in% c("sites", "biplot")) %>% # not sure what constraints are
#   left_join(microbialAbundance, by = c("Label" = "ID"))
# }
# 
# my_percent_explained <- function(ccaConstrained){
#   loc_anova <- anova(ccaConstrained, by = "margin")
#   loc_props <- loc_anova$ChiSquare/sum(loc_anova$ChiSquare)
#   loc_props_nr <- loc_props[1:(length(loc_props)-1)]
#   loc_props_nr
# }

My_Constrained_CCA_Plot_Type2 <- function(ccaConstrainedFort, ccaConstrained){
  ccaConstrainedPlot <- ccaConstrainedFort %>%
  filter(Score == "sites") %>%
  mutate(Depth = recode(Depth, `Oxy` = "Oxycline")) %>%
  select(Station, Depth, Size_Class, everything()) %>%
  ggplot(aes(x = CCA1, y = CA1,
             fill = as.factor(Station),
             shape = as.factor(Station),
             size = sqrt(Size_Class),
             color = as.factor(Depth)
             )) + 
 geom_point() +
 coord_fixed(sqrt(ccaConstrained$CA$eig[1]/ccaConstrained$CCA$eig[1])) +
 geom_label(aes(label = Label2, x = CCA1 * 2, y = CA1 * 2), color = "black", fill = "white", alpha = 0.6,
           data = ccaConstrainedFort %>%
             filter(Score == "biplot") %>%
             mutate(Label = recode(Label, lat = "Lat",
                                   `sqrt(Size_Class)` = "Size",
                                   `Depth2Surface` = "Surface"
                                   )) %>%
             mutate(PctExplained = my_percent_explained(ccaConstrained)) %>%
             mutate(Label2 = paste0(Label, "\n", round(PctExplained, 3) * 100, "%"))
             ) +
  geom_segment(aes(x = 0, y = 0, xend  = CCA1 * 1.7, yend = CA1 * 1.7), data = ccaConstrainedFort %>% filter(Score == "biplot"), inherit.aes = FALSE, size = 1, alpha = 0.25, arrow = arrow(length = unit(0.1, "in"))) +
  #geom_point(aes(x  = CCA1, y = CA1), data = ccaConstrainedFort %>% filter(Score == "biplot"), inherit.aes = FALSE) +
    labs(x = paste0("CCA1 (", round(ccaConstrained$CCA$eig[1]/ccaConstrained$tot.chi, 3) * 100, "%)"),
       y = paste0("CA1 (", round(ccaConstrained$CA$eig[1]/ccaConstrained$tot.chi, 3) * 100, "%)"),
       col = "Depth (Outline Color)",
       fill = "Station",
       shape = "Station",
       size = "Size Class") +
  myPlotDetails
ccaConstrainedPlot
}

My_Constrained_CCA_Plot_Type2_wFort <- function(ccaConstrained){
  ccaConstrainedFort <- my_fortify_function(ccaConstrained)
  My_Constrained_CCA_Plot_Type2(ccaConstrainedFort, ccaConstrained)
}
  
```

```{r}
AllSizePlotB <- My_Constrained_CCA_Plot_Type2_wFort(ccaConditionedAllSizes)
AllSizePlotB
```


## Minus free living stuff

```{r}
sampleData_NoFree <- sampleData01 %>% filter(Size_Class > 1)
wideASVs_log_NoFree <- wideASVs_log[rownames(wideASVs_log) %in% sampleData_NoFree$ID,]
wideASVs_log_NoFree <- wideASVs_log_NoFree[match(sampleData_NoFree$ID, rownames(wideASVs_log_NoFree)),]
# this is silly, I rearanged sample data last time time, but the ASV table this time
```

```{r}
ccaConditionedNoFree <- cca(wideASVs_log_NoFree ~ Condition(Depth2 + lat) + sqrt(Size_Class), data = sampleData_NoFree)
```

```{r}
CCA_Eigen_Plot(ccaConditionedNoFree)
```

```{r}
paste("Variance Explained", round(ccaConditionedNoFree$CCA$eig[1]/ccaConditionedNoFree$tot.chi, 3) * 100, "%")
anova(ccaConditionedNoFree, permutations = how(nperm = 10^3 - 1))
```

```{r}
My_Constrained_CCA_Plot(ccaConditionedNoFree)
```


## Minus 1.2 micron stuff


```{r}
sampleData_NoSmall <- sampleData01 %>% filter(Size_Class > 2)
wideASVs_log_NoSmall <- wideASVs_log[rownames(wideASVs_log) %in% sampleData_NoSmall$ID,]
wideASVs_log_NoSmall <- wideASVs_log_NoSmall[match(sampleData_NoSmall$ID, rownames(wideASVs_log_NoSmall)),]
# this is silly, I rearanged sample data last time time, but the ASV table this time
```

```{r}
ccaConditionedNoSmall <- cca(wideASVs_log_NoSmall ~ Condition(Depth2 + lat) + sqrt(Size_Class), data = sampleData_NoSmall)
```

```{r}
paste("Variance Explained", round(ccaConditionedNoSmall$CCA$eig[1]/ccaConditionedNoSmall$tot.chi, 3) * 100, "%")
anova(ccaConditionedNoSmall, permutations = how(nperm = 10^3 - 1))
```

```{r}
My_Constrained_CCA_Plot(ccaConditionedNoSmall)
```

Hahaha. Ok, now size is a factor, as I expected.
Maybe I was just underpowered with the surface only stuff?
Or the non-effect is only in the surface?

## Minus 1.2 micron stuff surface only


```{r}
sampleData_NoSmall <- sampleData01 %>% filter(Size_Class > 2) %>% filter(Depth == "Surface")
wideASVs_log_NoSmall <- wideASVs_log[rownames(wideASVs_log) %in% sampleData_NoSmall$ID,]
wideASVs_log_NoSmall <- wideASVs_log_NoSmall[match(sampleData_NoSmall$ID, rownames(wideASVs_log_NoSmall)),]
# this is silly, I rearanged sample data last time time, but the ASV table this time
```

```{r}
ccaConditionedNoSmall <- cca(wideASVs_log_NoSmall ~ Condition(lat) + sqrt(Size_Class), data = sampleData_NoSmall)
```

```{r}
paste("Variance Explained", round(ccaConditionedNoSmall$CCA$eig[1]/ccaConditionedNoSmall$tot.chi, 3) * 100, "%")
anova(ccaConditionedNoSmall, permutations = how(nperm = 10^3 - 1))
```

```{r}
My_Constrained_CCA_Plot(ccaConditionedNoSmall)
```

## Minus 1.2 micron stuff bottom only


```{r}
sampleData_NoSmall <- sampleData01 %>% filter(Size_Class > 2) %>% filter(Depth == "Bottom")
wideASVs_log_NoSmall <- wideASVs_log[rownames(wideASVs_log) %in% sampleData_NoSmall$ID,]
wideASVs_log_NoSmall <- wideASVs_log_NoSmall[match(sampleData_NoSmall$ID, rownames(wideASVs_log_NoSmall)),]
# this is silly, I rearanged sample data last time time, but the ASV table this time
```

```{r}
ccaConditionedNoSmall <- cca(wideASVs_log_NoSmall ~ Condition(lat) + sqrt(Size_Class), data = sampleData_NoSmall)
```

```{r}
paste("Variance Explained", round(ccaConditionedNoSmall$CCA$eig[1]/ccaConditionedNoSmall$tot.chi, 3) * 100, "%")
anova(ccaConditionedNoSmall, permutations = how(nperm = 10^3 - 1))
```

```{r}
My_Constrained_CCA_Plot(ccaConditionedNoSmall)
```

Too narrow. I'm calling it, size does matter.

# Lat and Depth Only
One more thing, I need to know the percent variance explained by just depth and latitude, so that I can show how much extra mileage size gets me.

```{r}
ccaConstrainedNoSize <- cca(wideASVs_log ~ lat + Depth2, data = sampleData01)
```

```{r}
ccaConstrainedNoSize
anova(ccaConstrainedNoSize, by = "margin")
```

```{r}
DepthLatPlot <- My_Constrained_CCA_Plot_Type1_wFort(ccaConstrainedNoSize)
DepthLatPlot
```

# For presentation
Plot of everything, followed by plot of Surf + Lat
Followed by size only.

```{r fig.height=4, fig.width=8}
twoCCAs <- plot_grid(DepthLatPlot + theme(legend.position = "none"),
          AllSizePlotB + theme(legend.position = "none"),
          get_legend(DepthLatPlot), nrow = 1, rel_widths = c(2,2,1))
twoCCAs
```

```{r}
ggsave("twoCCAs.png", twoCCAs, height = 5, width = 8)
```


# Thinking ahead
What about oxygen concentration as an explanatory variable?
What about interaction terms?

```{r}
ccaConstrainedProd <- cca(wideASVs_log ~ lat + Depth2 + sqrt(Size_Class) + (lat + Depth2) * sqrt(Size_Class), data = sampleData01)
```

```{r}
#ccaConstrainedProd <- cca(wideASVs_log ~ lat * Depth2 * sqrt(Size_Class), data = sampleData01)
```

```{r}
anova(ccaConstrainedProd, by = "margin")
```
Nothing noteable, assuming I ran this right. I was expecting some non interaction terms here too.
Maybe we just anova the highest level interactions.

```{r}
plot(ccaConstrainedProd)
```
The other terms are considered, so it looks like anova just does interactions.